---
title: "ASEM 2020 Image Recognition Analysis"
author: "Hari VS"
Date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
---
```{r include=FALSE}
library(tidyverse)
library(lmtest)
library(AICcmodavg)
library(broom)
library(ggpubr)
library(lsr)
library(rstatix)
library(knitr)
library(cowplot)
library(dplyr)
library(Hmisc)
library(FactoMineR)
library(multcompView)
library(lsmeans)
library(emmeans)
```


```{r echo=FALSE}
image_recog <- read.csv("Data_cleaned_person.csv")
```

Initial Summary Statistics
```{r}
summary(image_recog$Group)
summary(image_recog$college)
summary(image_recog$age)
summary(image_recog$gender)
summary(image_recog$task_difficulty_chr)
summary(image_recog$attn_check)
summary(image_recog$avg_conf)
```

The histograms shows the number of stimulis that were identified 
correctly by the participants. X axis represents the number of correct, 
y-axis represents the number of people in each range.
```{r echo=FALSE}
par(mfrow=c(2,2))

hist(image_recog$exact_match_answers_sum, main = "(a) Exact Match Accuracy",
     xlab = "No. of correct answers", ylab = "No. of participants",
     ylim = c(0,100), xlim = c(0,25))

hist(image_recog$synonym_answers_sum, main = "(b) Synonym Accuracy",
     xlab = "No. of correct answers", ylab = "No. of participants",
     ylim = c(0,100), xlim = c(0,25)) 

hist(image_recog$present_answers_sum, main = "(c) Present Accuracy",
     xlab = "No. of correct answers", ylab = "No. of participants",
     ylim = c(0,100), xlim = c(0,25)) 

hist(image_recog$category_answers_sum, main = "(d) Category Accuracy",
     xlab = "No. of correct answers", ylab = "No. of participants",
     ylim = c(0,100), xlim = c(0,25))

par(mfrow=c(1,1))
```

The histrogram shows the spread of the overall average confidence rating given
by the participants. The confidence rating is shown in 0 to 1 scale. 0 being 0%
and 1 being 100%. The response to thestimuli is also referred in 0s and 1s,
hence to maintain the uniformity, same scale was used for average confidence as
well.
```{r echo=FALSE}
par(mfrow=c(2,2))

hist(as.numeric(as.character(image_recog$avg_conf)), breaks = "FD",
     main = "(a) Confidence Rating", xlab = "Average Confidence")

round(sd(image_recog$avg_conf),2)
```

The average age of the participants was `r round(mean(image_recog$age),2)` years.
Standard deviation = `r round(sd(image_recog$age),2)` Youngest person to take the survey was `r round(min(image_recog$age),2)` years old.
Oldest person to take the survey was `r round(max(image_recog$age),2)` years old.
The age of the participants was not distributed evenly as it can be in the figure
below (left). Hence, age is log scaled after which the distribution is
relatively better. On all ANOVAs, the age was introduced as a variable in a log
scale.
```{r echo=FALSE}
par(mfrow=c(1,2))

hist(image_recog$age, main = "Age of Participants", xlab = "Age")

hist(log(image_recog$age), main = "Age of Participants on log scale",
     xlab = "Age log scaled")
```

The average time spent by the particpants per question was `r round(mean(image_recog$avg_time_spent_per_Q),2)` seconds (SD = `r round(sd(image_recog$avg_time_spent_per_Q),2)`) and ranged from `r round(min(image_recog$avg_time_spent_per_Q),2)` to `r round(max(image_recog$avg_time_spent_per_Q),2)` seconds.
Same reasoning goes for the time taken as age. The variable is introduced on a log scale
on all ANOVAs.
```{r echo=FALSE}
par(mfrow=c(1,2))

hist(image_recog$avg_time_spent_per_Q, main = "Average time per Question",
     xlab = "Time taken (s)")

hist(log(image_recog$avg_time_spent_per_Q), main = "Average time log scaled",
     xlab = "Time taken log scaled")
```

For task difficulty, the participants on average rated `r round(mean(image_recog$task_difficulty_chr_num),2)` with SD of `r round(sd(image_recog$task_difficulty_chr_num),2)`
```{r echo = FALSE}
image_recog$task_difficulty_chr <-
  factor(image_recog$task_difficulty_chr,
         levels(image_recog$task_difficulty_chr)[c(2,5,3,4,1)])


# table
tbl_task_difficulty_chr <- table(image_recog$task_difficulty_chr)
tbl_task_difficulty_chr

# graph
ggplot(image_recog, aes(x=task_difficulty_chr)) + geom_bar() + facet_wrap(~Group) +
  theme_bw(base_size = 18, base_family = "Times New Roman") +
  theme(axis.text.x = element_text(angle = 90, hjust =1)) +
  xlab("Task Difficulty Levels") + ylab("Count") + 
  ylim(0,30)
```


```{r}
par(mfrow=c(2,2))

hist(image_recog$exact_match_answers_as_percent, 
     main = "(a) Exact Match Accuracy", xlab = "No. of correct answers",
     ylab = "No. of participants", xlim = c(0,1))

hist(image_recog$synonym_answers_as_percent,
     main = "(b) Synonym Accuracy", xlab = "No. of correct answers",
     ylab = "No. of participants", xlim = c(0,1))

hist(image_recog$present_answers_as_percent,
     main = "(c) Present Accuracy", xlab = "No. of correct answers",
     ylab = "No. of participants", xlim = c(0,1)) 

hist(image_recog$category_answers_as_percent,
     main = "(d) Category Accuracy", xlab = "No. of correct answers",
     ylab = "No. of participants", xlim = c(0,1))

par(mfrow=c(1,1))
```

Exact Match Accuracy ANOVA
```{r echo=FALSE}
#First Step. One way ANOVA. 
#Looking at the effect of Group on Accuracy!

exact_one_way_anova <- aov(exact_match_answers_as_percent ~ Group,
                           data = image_recog)

summary(exact_one_way_anova)

eta_squared(exact_one_way_anova)
```


```{r}
exact_block_anova <- aov(exact_match_answers_as_percent ~ Group + avg_conf +
                           Task_difficulty_in_num + attn_check + 
                           avg_time_spent_per_Q + male_num + college + log(age),
                         data = image_recog)

summary(exact_block_anova)

eta_squared(exact_block_anova)
```

Exact Match Accuracy Post-Hoc Test
```{r echo=FALSE}
exact_models_set <- list(exact_one_way_anova)
exact_model_names <- c("exact_one_way_anova")
aictab(exact_models_set, modnames = exact_model_names)
```

Synonym Accuracy ANOVA
```{r echo=FALSE}
#First Step. One way ANOVA. 
#Looking at the effect of Group on Accuracy!

synonym_one_way_anova <- aov(synonym_answers_as_percent ~ Group,
                             data = image_recog)

summary(synonym_one_way_anova)

eta_squared(synonym_one_way_anova)
```


```{r}
synonym_block_anova <- aov(synonym_answers_as_percent ~ Group + avg_conf +
                           Task_difficulty_in_num + attn_check + 
                           avg_time_spent_per_Q + male_num + college + log(age),
                         data = image_recog)

summary(synonym_block_anova)

eta_squared(synonym_block_anova)
```

Synonym Accuracy Post-Hoc Test
```{r echo=FALSE}
synonym_models_set <- list(synonym_one_way_anova)
synonym_model_names <- c("synonym_one_way_anova")
aictab(synonym_models_set, modnames = synonym_model_names)
```



```{r}
present_block_anova <- aov(present_answers_as_percent ~ Group + avg_conf +
                           Task_difficulty_in_num + attn_check + 
                           avg_time_spent_per_Q + male_num + college + log(age),
                         data = image_recog)

summary(present_block_anova)

eta_squared(present_block_anova)
```



Present Accuracy ANOVA
```{r echo=FALSE}
#First Step. One way ANOVA. 
#Looking at the effect of Group on Accuracy!

present_one_way_anova <- aov(present_answers_as_percent ~ Group,
                             data = image_recog)

summary(present_one_way_anova)

eta_squared(present_one_way_anova)
```

present Accuracy Post-Hoc Test
```{r echo=FALSE}
present_models_set <- list(present_one_way_anova)
present_model_names <- c("present_one_way_anova")
aictab(present_models_set, modnames = present_model_names)
```

Category Accuracy ANOVA
```{r echo=FALSE}
#First Step. One way ANOVA. 
#Looking at the effect of Group on Accuracy!

category_one_way_anova <- aov(category_answers_as_percent ~ Group, 
                              data = image_recog)
summary(category_one_way_anova)

eta_squared(category_one_way_anova)
```



```{r}
category_block_anova <- aov(category_answers_as_percent ~ Group + avg_conf +
                           Task_difficulty_in_num + attn_check + 
                           avg_time_spent_per_Q + male_num + college + log(age),
                         data = image_recog)

summary(category_block_anova)

eta_squared(category_block_anova)
```


category Accuracy Post-Hoc Test
```{r echo=FALSE}
category_models_set <- list(category_one_way_anova)
category_model_names <- c("category_one_way_anova")
aictab(category_models_set, modnames = category_model_names)
```

PLotting the QQ plots for all of the ANOVAs
```{r echo=FALSE}
par(mfrow=c(2,2))

plot(exact_one_way_anova, which = 2) + title("(a) Exact Accuracy", line = 1.35)

plot(synonym_one_way_anova, which = 2) +
  title("(b) Synonym Accuracy", line = 1.35)

plot(present_one_way_anova, which = 2) +
  title("(c) Present Accuracy", line = 1.35)

plot(category_one_way_anova, which = 2) +
  title("(d) Category Accuracy", line = 1.35)

par(mfrow=c(1,1))
```

```{r echo=FALSE}
#Exact Match Accuracy Tukey Test
exact_tukey_interaction <- TukeyHSD(exact_one_way_anova, which = "Group")
exact_tukey_interaction

#Synonym Accuracy Tukey Test
synonym_tukey_interaction <- TukeyHSD(synonym_one_way_anova, which = "Group")
synonym_tukey_interaction

#Present Accuracy Tukey Test
present_tukey_interaction <- TukeyHSD(present_one_way_anova, which = "Group")
present_tukey_interaction

#Category Accuracy Tukey Test
category_tukey_interaction <- TukeyHSD(category_one_way_anova, which = "Group")
category_tukey_interaction
```


```{r echo=FALSE}
par(mfrow=c(2,2))

plot(exact_tukey_interaction, las=1, yaxt= "none") + 
  title("(a) Exact Accuracy", line = 0.35)
axis(2, at=15:1, las =1)

plot(synonym_tukey_interaction, las=1, yaxt= "none") + 
  title("(b) Synonym Accuracy", line = 0.35)
axis(2, at=15:1, las =1)

plot(present_tukey_interaction, las=1, yaxt= "none") +
  title("(c) Present Accuracy", line = 0.35)
axis(2, at=15:1, las =1)
plot(category_tukey_interaction, las=1, yaxt= "none") + 
  title("(d) Category Accuracy", line = 0.35)
axis(2, at=15:1, las =1)

par(mfrow=c(1,1))
```



```{r }
#Exact Match Accuracy rcorr tables.
all_rcorr <- rcorr(as.matrix(image_recog[,c("exact_match_answers_as_percent",
                                            "synonym_answers_as_percent",
                                            "present_answers_as_percent",
                                            "category_answers_as_percent",
                                            "avg_conf", "One_AI_bar",
                                            "One_AI_nobar","Five_AI_bar",
                                            "Five_AI_nobar","Five_AI_ABC",
                                            "college","age",
                                            "Task_difficulty_in_num", 
                                            "male_num", "avg_time_spent_per_Q",
                                            "attn_check")]))

all_rcorr
```

All accuracies Average Confidence ANOVA
```{r echo=FALSE}
one_way_anova_avg_conf <- aov(avg_conf ~ Group, data = image_recog)

summary(one_way_anova_avg_conf)

models_set_avg_conf <- list(one_way_anova_avg_conf)
model_names_avg_conf <- c("one_way_anova_avg_conf")
aictab(models_set_avg_conf, modnames = model_names_avg_conf)

#Average Confidence Tukey Test
tukey_interaction_avg_conf <- TukeyHSD(one_way_anova_avg_conf, which = "Group")
plot(tukey_interaction_avg_conf, las=1)+ title("Avg Confidence", line = 0.35)
```


```{r}
#One-way ANOVA Task Difficulty
one_way_anova_task_difficulty <- aov(Task_difficulty_in_num ~ Group,
                                     data = image_recog)

summary(one_way_anova_task_difficulty)

#Post-hoc test
models_set_task_difficulty <- list(one_way_anova_task_difficulty)
model_names_task_difficulty <- c("one_way_anova_task_difficulty")
aictab(models_set_task_difficulty, modnames = model_names_task_difficulty)

#Tukey HSD Interaction
tukey_interaction_task_difficulty <- TukeyHSD(one_way_anova_task_difficulty,
                                              which = "Group")

tukey_interaction_task_difficulty

#Plot of Tukey Interaction
plot(tukey_interaction_task_difficulty, las=1)+ title("Task Difficulty",
                                                      line = 0.35)
```



```{r}
#One-way ANOVA Avergae time spent per image
one_way_anova_avg_time_per_image <- aov(avg_time_spent_per_Q ~ Group,
                                        data = image_recog)

summary(one_way_anova_avg_time_per_image)

#Post-hoc test
models_set_avg_time_per_image <- list(one_way_anova_avg_time_per_image)
model_names_avg_time_per_image <- c("one_way_anova_avg_time_per_image")
aictab(models_set_avg_time_per_image, modnames = model_names_avg_time_per_image)

#Tukey HSD Interaction
tukey_interaction_avg_time_per_image <- 
  TukeyHSD(one_way_anova_avg_time_per_image, which = "Group")

tukey_interaction_avg_time_per_image

#Plot of Tukey Interaction
plot(tukey_interaction_avg_time_per_image, las=1, yaxt= "none") +
  title("Average Time Spent Per Image", line = 0.35)
axis(2, at=15:1, las =1)
```


```{r echo=FALSE}
#Exact Match Accuracy - Accuracy vs Group plot with errorbars
exact_conditions_summary <- image_recog %>%
  group_by(Group) %>%
  summarise(mean_answer = mean(exact_match_answers_as_percent, na.rm = TRUE),
            sd_answer = sd(exact_match_answers_as_percent, na.rm = TRUE))

#Synonym Accuracy - Accuracy vs Group plot with errorbars
synonym_conditions_summary <- image_recog %>%
  group_by(Group) %>%
  summarise(mean_answer = mean(synonym_answers_as_percent, na.rm = TRUE),
            sd_answer = sd(synonym_answers_as_percent, na.rm = TRUE))

#Present Accuracy - Accuracy vs Group plot with errorbars
present_conditions_summary <- image_recog %>%
  group_by(Group) %>%
  summarise(mean_answer = mean(present_answers_as_percent, na.rm = TRUE),
            sd_answer = sd(present_answers_as_percent, na.rm = TRUE))

#Category Accuracy - Accuracy vs Group plot with errorbars
category_conditions_summary <- image_recog %>%
  group_by(Group) %>%
  summarise(mean_answer = mean(category_answers_as_percent, na.rm = TRUE),
            sd_answer = sd(category_answers_as_percent, na.rm = TRUE))

image_recog$Group <- factor(image_recog$Group, 
                                        levels(image_recog$Group)[c(6,2,1,3,5,4)])


exact_summ_plot <- ggplot(exact_conditions_summary, aes(y=mean_answer,
                                                        x=Group)) + 
  geom_bar(position="dodge", stat="identity", width = 0.5)+ 
  geom_errorbar(aes(ymin= mean_answer - sd_answer, 
                    ymax= mean_answer + sd_answer), width=.2) +
  theme_bw(base_size = 18, base_family = "Times New Roman") + 
  theme(axis.text.x = element_text(angle = 90, hjust =1)) +
  xlab("Experimental Conditions") + ylab("Mean Performance") + 
  ylim(0,1) + 
  ggtitle("(a) Exact Match Accuracy")

synonym_summ_plot <- ggplot(synonym_conditions_summary, aes(y=mean_answer,
                                                            x=Group)) + 
  geom_bar(position="dodge", stat="identity", width = 0.5)+ 
  geom_errorbar(aes(ymin= mean_answer - sd_answer, 
                    ymax= mean_answer + sd_answer), width=.2) +
  theme_bw(base_size = 18, base_family = "Times New Roman") + 
  theme(axis.text.x = element_text(angle = 90, hjust =1)) +
  xlab("Experimental Conditions") + ylab("Mean Performance") + 
  ylim(0,1) + 
  ggtitle("(b) Synonym Accuracy")

present_summ_plot <- ggplot(present_conditions_summary, aes(y=mean_answer,
                                                            x=Group)) + 
  geom_bar(position="dodge", stat="identity", width = 0.5)+ 
  geom_errorbar(aes(ymin= mean_answer - sd_answer, 
                    ymax= mean_answer + sd_answer), width=.2) +
  theme_bw(base_size = 18, base_family = "Times New Roman") + 
  theme(axis.text.x = element_text(angle = 90, hjust =1)) +
  xlab("Experimental Conditions") + ylab("Mean Performance") + 
  ylim(0,1) + 
  ggtitle("(c) Present Accuracy")

category_summ_plot <- ggplot(category_conditions_summary, aes(y=mean_answer,
                                                              x=Group)) + 
  geom_bar(position="dodge", stat="identity", width = 0.5)+ 
  geom_errorbar(aes(ymin= mean_answer - sd_answer, 
                    ymax= mean_answer + sd_answer), width=.2) +
  theme_bw(base_size = 18, base_family = "Times New Roman") + 
  theme(axis.text.x = element_text(angle = 90, hjust =1)) +
  xlab("Experimental Conditions") + ylab("Mean Performance") + 
  ylim(0,1) + 
  ggtitle("(d) Category Accuracy")

plot_grid(exact_summ_plot, synonym_summ_plot, present_summ_plot, category_summ_plot)
```


```{r}
# Two-Way Anova
# REF: https://rcompanion.org/rcompanion/d_08.html
model_lm <- lm(exact_match_answers_as_percent ~ AI_1or5 + bar + AI_1or5:bar,
               data = image_recog_AI1or5)

summary(model_lm) # not significant in lm
Anova(model_lm, type="II") # AI_1or5 sig in ANOVA
anova(model_lm)

# simple comparison of means
by(image_recog_AI1or5$exact_match_answers_as_percent, 
   image_recog_AI1or5$AI_1or5, function(x) {round(mean(x),2)})

# simple comparison of standard deviation
by(image_recog_AI1or5$exact_match_answers_as_percent, image_recog_AI1or5$AI_1or5,
   function(x) {round(sd(x),4)})

# Mean separations for main factor with lsmeans
lsmeans = lsmeans::lsmeans
leastsquare = lsmeans(model_lm, "AI_1or5", adjust="tukey")
```

AI_1or5 is marginally significant (right around the  p = .05 level). This
suggests that there may be a significant difference between 1AI vs. 5AI
(5AI is slightly higher at M = 0.50 vs. M = 0.47). The effect of bar is not
significant, suggesting that there is no difference between including the bars
or not. The interaction between number of recommendations and bars is also not
significant.
```{r}
# Two-Way Anova
# REF: https://rcompanion.org/rcompanion/d_08.html
model_lm2 <- lm(synonym_answers_as_percent ~ AI_1or5 + bar + AI_1or5:bar,
                data = image_recog_AI1or5)

summary(model_lm2) # not significant in lm
Anova(model_lm2, type="II") # AI_1or5 sig in ANOVA
anova(model_lm2)

# simple comparison of means
by(image_recog_AI1or5$synonym_answers_as_percent, image_recog_AI1or5$AI_1or5,
   function(x) {round(mean(x),2)})

# simple comparison of standard deviation
by(image_recog_AI1or5$synonym_answers_as_percent, image_recog_AI1or5$AI_1or5,
   function(x) {round(sd(x),4)})

# Mean separations for main factor with lsmeans
lsmeans = lsmeans::lsmeans
leastsquare2 = lsmeans(model_lm2, "AI_1or5", adjust="tukey")
```



```{r}
# Two-Way Anova
# REF: https://rcompanion.org/rcompanion/d_08.html
model_lm3 <- lm(present_answers_as_percent ~ AI_1or5 + bar + AI_1or5:bar,
                data = image_recog_AI1or5)

summary(model_lm3) # not significant in lm
Anova(model_lm3, type="II") # AI_1or5 sig in ANOVA
anova(model_lm3)

# simple comparison of means
by(image_recog_AI1or5$present_answers_as_percent, image_recog_AI1or5$AI_1or5,
   function(x) {round(mean(x),2)})

# simple comparison of standard deviation
by(image_recog_AI1or5$present_answers_as_percent, image_recog_AI1or5$AI_1or5,
   function(x) {round(sd(x),4)})

# Mean separations for main factor with lsmeans
lsmeans = lsmeans::lsmeans
leastsquare3 = lsmeans(model_lm3, "AI_1or5", adjust="tukey")
```



```{r}
# Two-Way Anova
# REF: https://rcompanion.org/rcompanion/d_08.html
model_lm4 <- lm(category_answers_as_percent ~ AI_1or5 + bar + AI_1or5:bar,
                data = image_recog_AI1or5)

summary(model_lm4) # not significant in lm
Anova(model_lm4, type="II") # AI_1or5 sig in ANOVA
anova(model_lm4)

# simple comparison of means
by(image_recog_AI1or5$category_answers_as_percent, image_recog_AI1or5$AI_1or5,
   function(x) {round(mean(x),2)})

# simple comparison of standard deviation
by(image_recog_AI1or5$category_answers_as_percent, image_recog_AI1or5$AI_1or5,
   function(x) {round(sd(x),4)})

# Mean separations for main factor with lsmeans
lsmeans = lsmeans::lsmeans
leastsquare4 = lsmeans(model_lm4, "AI_1or5", adjust="tukey")
```

1. It appears that the bar does not have an effect at all; irrespective of the definition of the accuracy. 
2. AI_1or5 is marginally significant
3. Overall, 5AI has a higher simple Mean compared to 1AI in all accuracies: (M = M of 5AI (M of 1AI))
(M = 0.50(0.47), M = 0.61(0.57), M = 0.68(0.64), M = 0.79(0.75))
4. The interaction between 1AI&5AI and Bar is also not significant in any of the accuracies.
5. Since no interaction was signifcant, no one-way ANOVA for all of our factors is necessary.

Since there is no effect of bar or the interaction of AI and bar, we can accept to NULL hypothesis.
1. The means are the same for bar and no bar
2. Since interaction shows no effect, it means, the performance of people in 1AI or 5AI does not depend on bars or viceversa.


```{r}
#Exact Match Accuracy - Accuracy vs Group plot with errorbars
exact_conditions_summary2 <- image_recog_AI1or5 %>%
  group_by(AI_1or5) %>%
  summarise(mean_answer = mean(exact_match_answers_as_percent, na.rm = TRUE),
            sd_answer = sd(exact_match_answers_as_percent, na.rm = TRUE))

#Synonym Accuracy - Accuracy vs Group plot with errorbars
synonym_conditions_summary2 <- image_recog_AI1or5 %>%
  group_by(AI_1or5) %>%
  summarise(mean_answer = mean(synonym_answers_as_percent, na.rm = TRUE),
            sd_answer = sd(synonym_answers_as_percent, na.rm = TRUE))

#Present Accuracy - Accuracy vs Group plot with errorbars
present_conditions_summary2 <- image_recog_AI1or5 %>%
  group_by(AI_1or5) %>%
  summarise(mean_answer = mean(present_answers_as_percent, na.rm = TRUE),
            sd_answer = sd(present_answers_as_percent, na.rm = TRUE))

#Category Accuracy - Accuracy vs Group plot with errorbars
category_conditions_summary2 <- image_recog_AI1or5 %>%
  group_by(AI_1or5) %>%
  summarise(mean_answer = mean(category_answers_as_percent, na.rm = TRUE),
            sd_answer = sd(category_answers_as_percent, na.rm = TRUE))


exact_summ_plot2 <- ggplot(exact_conditions_summary2, aes(y=mean_answer,
                                                        x=AI_1or5)) + 
  geom_bar(position="dodge", stat="identity", width = 0.5)+ 
  geom_errorbar(aes(ymin= mean_answer - sd_answer, 
                    ymax= mean_answer + sd_answer), width=.2) +
  theme_bw(base_size = 18, base_family = "Times New Roman") + 
  theme(axis.text.x = element_text(angle = 90, hjust =1)) +
  xlab("Experimental Conditions") + ylab("Mean Performance") + 
  ylim(0,1) + 
  ggtitle("(a) Exact Match Accuracy")

synonym_summ_plot2 <- ggplot(synonym_conditions_summary2, aes(y=mean_answer,
                                                            x=AI_1or5)) + 
  geom_bar(position="dodge", stat="identity", width = 0.5)+ 
  geom_errorbar(aes(ymin= mean_answer - sd_answer, 
                    ymax= mean_answer + sd_answer), width=.2) +
  theme_bw(base_size = 18, base_family = "Times New Roman") + 
  theme(axis.text.x = element_text(angle = 90, hjust =1)) +
  xlab("Experimental Conditions") + ylab("Mean Performance") + 
  ylim(0,1) + 
  ggtitle("(b) Synonym Accuracy")

present_summ_plot2 <- ggplot(present_conditions_summary2, aes(y=mean_answer,
                                                            x=AI_1or5)) + 
  geom_bar(position="dodge", stat="identity", width = 0.5)+ 
  geom_errorbar(aes(ymin= mean_answer - sd_answer, 
                    ymax= mean_answer + sd_answer), width=.2) +
  theme_bw(base_size = 18, base_family = "Times New Roman") + 
  theme(axis.text.x = element_text(angle = 90, hjust =1)) +
  xlab("Experimental Conditions") + ylab("Mean Performance") + 
  ylim(0,1) + 
  ggtitle("(c) Present Accuracy")

category_summ_plot2 <- ggplot(category_conditions_summary2, aes(y=mean_answer,
                                                              x=AI_1or5)) + 
  geom_bar(position="dodge", stat="identity", width = 0.5)+ 
  geom_errorbar(aes(ymin= mean_answer - sd_answer, 
                    ymax= mean_answer + sd_answer), width=.2) +
  theme_bw(base_size = 18, base_family = "Times New Roman") + 
  theme(axis.text.x = element_text(angle = 90, hjust =1)) +
  xlab("Experimental Conditions") + ylab("Mean Performance") + 
  ylim(0,1) + 
  ggtitle("(d) Category Accuracy")

plot_grid(exact_summ_plot2, synonym_summ_plot2, present_summ_plot2, category_summ_plot2)
```


