---
title: "Data Cleaning"
author: "Hari VS"
Date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
---

Notes from Canfield code review:
* Use comments to explain what your code is doing
* Use the white part of the R Notebook to create sections and explain what you
  are doing 
(see https://rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)

***

Purpose: This code cleans the raw Qualtrics output and organizes the data in
three different structures:

1. **data_person** where each row is a single person
2. **data_image** where each row is a single image
3. **data_person_image** where row is a single person for a single image and
there are 24 rows per person

### IMPORT DATA

```{r}
# Load libraries
library(tidyverse)
library(broom)
library(Hmisc)
library(ggimage)
library(gridExtra)
library(car)
library(dplyr)
library(lubridate)
library(utils)
```




```{r}
# import raw data from Qualtrics
raw_data <- read_csv("Qualtrics_data_05.13.2020.csv")

#copying data so originial is left untouched
data_person <- raw_data 

#Converting class of the timestamps
data_person$StartDate <-  as_datetime(data_person$StartDate)

#started collecting data on 5/1/20 at 2:39 PM
data_person <- filter(data_person, StartDate >= #select cells
                        as.POSIXct("2020-05-01 14:39:00", #that has timestamps past 2:39 PM on May 1st
                                   tz = "UTC")) %>% #timestamps are in Mountrain TimeZone
  filter(Finished == "True") #removing incomplete surveys

#Removing unwanted columns
data_person <- select(data_person, "StartDate","Duration (in seconds)", #Specifying column names
                      "Finished", "ResponseId","Q6":"mTurkCode" ) #Select columns from Q6 to mTurkCode

# remove unused factor levels
data_person <- droplevels(data_person)

# convert to tibble
data_person <- as_tibble(data_person)

#Removing columns that has NAs for all cells
all_na <- function(x){
  any(!is.na(x)) #anything is that not NA.
#write the names of the columns.
} 

#Applying the all_na funtion to data_person tibble
data_person <- data_person[, #chossing columns from the data frame
                           which( #mentioning which columns
                             unlist( #drop the one that follows lapply
                               lapply(data_person,all_na)))]
                               #lapply tells to apply all_na function

#Removing more unwanted columns
data_person <- data_person %>% 
  select(-contains("Click")) #These columns are not needed
#These columns recorded the first click and last click time (in seconds) for
  #every stimuli. It also recorded click counts for all. 

#Removing duplicate column
data_person <- data_person %>% #Duplicate column that stores participant ID.
  select(- "Q274") #Column named PROLIFIC_PID has same information.

#Removing unwanted column
data_person <- data_person %>% #No one had a time limit to answer
  select(- c(TimeLimit)) #unwanted column

#Removing unwanted column
data_person <- data_person %>% #unwanted confidence information
  select(- c(Q485_1)) #Howler monkey confidence rating.

#Removing unwanted column
data_person <- data_person %>% #No one had a time limit to answer
  select(- c(`Q490_Page Submit`)) #unwanted column
```


### Renaming Columns

```{r}
#Renaming Consent Columns
data_person <- data_person %>% 
  rename( #renaming columns
    Consent1_chr = Q6, #Original column name goes on the right.
    Consent2_chr = Q8
    )

#Renaming Initial Attention Checks 
data_person <- data_person %>%
  rename(
    Attn_check1_chr = Q467,
    Attn_check2_chr = Q468,
  )

#Renaming demographics columns
data_person <- data_person %>%
  rename(
    year_born = Q89,
    education_chr = Q93,
    gender_chr = Q91,
    AI_trustworthy_chr = Q514,
    task_difficulty_chr = Q87,
    AI_help_count = Q269_1
    )

#Renaming Feedback column
data_person <- data_person %>% 
  rename(
    Feedback = Q95) #Manual feedback entered by participants.
```


```{r}
#Renaming columns corresponding to Time spent in each question
data_person <- data_person %>%
  rename(
    sea_slug_time = `Q98_Page Submit`,
    swimming_trunks_time = `Q363_Page Submit`,
    megalith_time = `Q372_Page Submit`,
    brown_bear_time = `Q477_Page Submit`,
    nails_time = `Q520_Page Submit`,
    chickpea_time = `Q640_Page Submit`,
    goblet_time = `Q658_Page Submit`,
    monitor_time = `Q667_Page Submit`,
    spider_monkey_time = `Q676_Page Submit`, 
    gazania_time = `Q685_Page Submit`,
    marimba_time = `Q694_Page Submit`,
    football_helmet_time = `Q739_Page Submit`,
    madagascar_cat_time = `Q766_Page Submit`,
    shrimp_time = `Q775_Page Submit`,
    mite_time = `Q793_Page Submit`,
    nightsnake_time = `Q811_Page Submit`,
    basenji_time = `Q820_Page Submit`,
    vacuum_time = `Q838_Page Submit`,
    cherry_time = `Q856_Page Submit`,
    ruffed_grouse_time = `Q865_Page Submit`,
    metronome_time = `Q883_Page Submit`,
    envelope_time = `Q910_Page Submit`,
    logwood_time = `Q919_Page Submit`,
    fragrant_orchid_time = `Q937_Page Submit`
  )
```


```{r}
#renaming columns that correspond to Stimuli names
data_person <- data_person %>%
  rename(
    sea_slug_resp = Q97,
    swimming_trunks_resp = Q370,
    megalith_resp = Q379,
    brown_bear_resp = Q484,
    nails_resp = Q527,
    chickpea_resp = Q647,
    goblet_resp = Q665,
    monitor_resp = Q674,
    spider_monkey_resp = Q683,
    gazania_resp = Q692,
    marimba_resp = Q701,
    football_helmet_resp = Q746,
    madagascar_cat_resp = Q773,
    shrimp_resp = Q782,
    mite_resp = Q800,
    nightsnake_resp = Q818,
    basenji_resp = Q827,
    vacuum_resp = Q845,
    cherry_resp = Q863,
    ruffed_grouse_resp = Q872,
    metronome_resp = Q890,
    envelope_resp = Q917,
    logwood_resp = Q926,
    fragrant_orchid_resp = Q944,
    howler_monkey_resp = Q483
)
```


```{r}
#renaming columns corresponding to confidence ratings of each stimilus.

data_person <- data_person %>%
  rename(
    sea_slug_conf = Q97_1,
    swimming_trunks_conf = Q371,
    megalith_conf = Q380,
    brown_bear_conf = Q485,
    nails_conf = Q528,
    chickpea_conf = Q648,
    goblet_conf = Q666,
    monitor_conf = Q675,
    spider_monkey_conf = Q684,
    gazania_conf = Q693,
    marimba_conf = Q702,
    football_helmet_conf = Q747,
    madagascar_cat_conf = Q774,
    shrimp_conf = Q783,
    mite_conf = Q801,
    nightsnake_conf = Q819,
    basenji_conf = Q828,
    vacuum_conf = Q846,
    cherry_conf = Q864,
    ruffed_grouse_conf = Q873,
    metronome_conf = Q891,
    envelope_conf = Q918,
    logwood_conf = Q927,
    fragrant_orchid_conf = Q945,
  )
```


```{r}
#Reodering columns for ease of analysis
data_person <- data_person[ c("AI_trustworthy_chr",
  "task_difficulty_chr","AI_help_count", "Feedback",
  "StartDate","Duration (in seconds)","Finished", "ResponseId",
  "PROLIFIC_PID", "mTurkCode","year_born","gender_chr","education_chr","Group",
  "Consent1_chr","Consent2_chr","Attn_check1_chr","Attn_check2_chr",
  "sea_slug_resp", "swimming_trunks_resp", "megalith_resp", 
  "brown_bear_resp", "nails_resp", "chickpea_resp", "goblet_resp",
  "monitor_resp", "spider_monkey_resp", "gazania_resp", "marimba_resp",
  "football_helmet_resp", "madagascar_cat_resp", "shrimp_resp",
  "mite_resp", "nightsnake_resp", "basenji_resp", "vacuum_resp",
  "cherry_resp", "ruffed_grouse_resp", "metronome_resp", "envelope_resp",
  "logwood_resp", "fragrant_orchid_resp", "howler_monkey_resp",
  "sea_slug_conf","swimming_trunks_conf","megalith_conf","brown_bear_conf",
  "nails_conf","chickpea_conf","goblet_conf","monitor_conf","spider_monkey_conf",
  "gazania_conf","marimba_conf","football_helmet_conf","madagascar_cat_conf","shrimp_conf",
  "mite_conf","nightsnake_conf","basenji_conf","vacuum_conf","cherry_conf",
  "ruffed_grouse_conf","metronome_conf","envelope_conf","logwood_conf",
  "fragrant_orchid_conf","sea_slug_time",
  "swimming_trunks_time", "megalith_time","brown_bear_time", "nails_time",
  "chickpea_time", "goblet_time","monitor_time", "spider_monkey_time",
  "gazania_time","marimba_time", "football_helmet_time", "madagascar_cat_time",
  "shrimp_time", "mite_time", "nightsnake_time", "basenji_time","vacuum_time",
  "cherry_time", "ruffed_grouse_time","metronome_time", "envelope_time",
  "logwood_time","fragrant_orchid_time")]
```




### DEMOGRAPHICS

Explain what corrections you made to the data and why
Hardcoding like this is dangerous - it's easy for the data to get messed up. It's better to pull based on the actual values. See code below.


```{r}
#AGE
#convert to numeric
data_person$year_born <- as.numeric(data_person$year_born)

# corrected typos in data
data_person$year_born[data_person$year_born == 83] <- 1983 # said 83
data_person$year_born[data_person$year_born == 193] <- 1993 # said 193

# some participants reported their age instead of year born
data_person$year_born <- ifelse(data_person$year_born < 1000, # if value < 1000
                                2020 - data_person$year_born, # subtract from 2020
                                data_person$year_born) # otherwise, leave it alone

# calculate age
data_person$age <- 2020 - data_person$year_born #numeric class
```
Cleaned the responses given by the participants when asked "What year were you
born?". Some of them gave their age instead of the year. Some responsed with 
text which are replaced with NAs.



```{r}
# EDUCATION
data_person$college <- case_when(data_person$education_chr == "4 year degree" ~ 1,
                              data_person$education_chr == "Professional degree" ~ 1,
                              data_person$education_chr == "Doctorate" ~ 1,
                              data_person$education_chr == "2 year degree" ~ 0,
                              data_person$education_chr == "Some college" ~ 0,
                              data_person$education_chr == "High School" ~ 0)

# gender dummy
data_person$male_num <- ifelse(data_person$gender_chr == "Male",1,0)
```
Participants chose one of six options for their education. To numerically 
record education, participants who graduated at least with Bachelors were 
given one (1). Zero (0) was assigned to participants who do not have a 
four-year college degree or more.


### EXPERIMENTAL MANIPULATION


```{r}
# AI TRUST
# numeric version
data_person$AI_trustworthy_in_num <- case_when( 
  #case_when: if response is equal to "x", assign "y"
  data_person$AI_trustworthy_chr == "Very untrustworthy" ~ 1,
  data_person$AI_trustworthy_chr == "Somewhat untrustworthy" ~ 2,
  data_person$AI_trustworthy_chr == "I don't know" ~ 3,
  data_person$AI_trustworthy_chr == "Somewhat trustworthy" ~ 4,
  data_person$AI_trustworthy_chr == "Very trustworthy" ~ 5
)

# TASK DIFFICULTY
# numeric version
data_person$Task_difficulty_in_num <- case_when(
  #case_when: if response is equal to "x", assign "y"
  data_person$task_difficulty_chr == "Extremely easy" ~ 1,
  data_person$task_difficulty_chr == "Somewhat easy" ~ 2,
  data_person$task_difficulty_chr == "I don't know" ~ 3,
  data_person$task_difficulty_chr == "Somewhat difficult" ~ 4,
  data_person$task_difficulty_chr == "Extremely difficult" ~ 5
)

# AI HELP
#converting class to numeric
data_person$AI_help_count <- as.numeric(data_person$AI_help_count)

data_person$AI_help_percent <- data_person$AI_help_count/max(data_person$AI_help_count, na.rm=TRUE)
```
Participants were asked questions at the end with regards to the survey.
AI TRUSTWORTHY shows how people felt about AI's recommendations.
Task DIFFICULTY indicated how people felt above the whole survey.
AI HELP indicates how many times the AI was helpful with it's recommendations.
All three questions were categorical (i.e. people chose one of the options)


```{r}
# CONDITIONS
# dummy variables
data_person$One_AI_bar <- ifelse(data_person$Group == "1AI_bar", 1, 0)
data_person$One_AI_nobar <- ifelse(data_person$Group == "1AI_nobar", 1, 0)
data_person$Five_AI_bar <- ifelse(data_person$Group == "5AI_bar",1, 0)
data_person$Five_AI_nobar <- ifelse(data_person$Group == "5AI_nobar",1, 0)
data_person$Five_AI_ABC <- ifelse(data_person$Group == "5AI_ABC",1,0)
data_person$Control <- ifelse(data_person$Group == "Control",1,0)
#If Participants were in Control Group, assign 1, else 0.

# summary dummy variables
data_person$AI <- ifelse(data_person$Group != "Control", 1, 0)
#Control Group did not receive AI help. If Partcipants were not in Control
#group, assign 1, else 0.
data_person$One_AI <- ifelse(data_person$Group == "1AI_bar", 1, 
                             ifelse(data_person$Group == "1AI_nobar",1,0))
#If Participants received only one AI recommendation, assign 1, esle 0.

data_person$Five_AI <- ifelse(data_person$Group == "5AI_bar", 1, 
                             ifelse(data_person$Group == "5AI_nobar",1,
                                    ifelse(data_person$Group == "5AI_ABC",1,0)))
#If Participants received five AI recommendations, assign 1, esle 0.

data_person$bar <- ifelse(data_person$Group == "1AI_bar", 1, 
                             ifelse(data_person$Group == "5AI_bar",1,0))
#If participants received confidence bars for the recommendatio from AI, 
#assign 1, else 0

data_person$nobar <- ifelse(data_person$Group == "1AI_nobar", 1, 
                             ifelse(data_person$Group == "5AI_nobar",1,
                                    ifelse(data_person$Group == "5AI_ABC",1,0)))
#If participants did not receieve confidence bars for the recommendation from AI
#assign 1, else 0.
```
Participants of the survey were randomly placed on one of six experimental
conditions mentioned above. Above chunk was used to represent them in dummy
varibales for ease of analysis. 



### STIMULI

Answers were manually coded to determine the category of correctness

```{r}
# the coding is included in a separate R file
source("Stimuli_response_coding.R")
```

```{r}
#ATTN CHECK
# individual attention checks
data_person$attn_check1_num <- 
  ifelse(data_person$Attn_check1_chr == "Howler Monkey",1, 0)
data_person$attn_check2_num <- 
  ifelse(data_person$Attn_check2_chr == "Be Specific",1, 0)
data_person$attn_check3_num <- 
  ifelse(data_person$howler_monkey == "correct",1, 0)

# sum
data_person$attn_check_sum <- rowSums(data_person %>%
                                        select(attn_check1_num:attn_check3_num))
#One column to represent how many of the three attention checks did the
#participant respond to correctly.

# binary indicator
data_person$attn_check <- 
  ifelse(data_person$attn_check1_num == 1 &
           data_person$attn_check2_num == 1 &
           data_person$attn_check3_num == 1,1, 0)
#If the participant responded to all three questions correctly,assign 1,else 0
```
Participants of the survey were asked a sum of three attnetion checks.
First two attention checks were in the beginning of the survey. They were given
a categorical question. Last question was text input. Participant had to type
the answer manually. 


```{r}
# CONFIDENCE

#creating a function to replace chr as numerics.
#representing confidence in 0-1 scale because all other varibales are
#also represented in terms of 0s and 1s.
confidence_to_num <- function(x){
case_when(  
  #case_when: if response is equal to "x", assign "y"
  x == "0% Confident" ~ 0,
  x == "20% Confident" ~ .2,
  x == "40% Confident" ~ .4,
  x == "60% Confident" ~ .6,
  x == "80% Confident" ~ .8,
  x ==  "100% Confident" ~ 1)}

data_person <- data_person %>% #choosing tibble
  mutate_at(.vars = vars(sea_slug_conf: fragrant_orchid_conf), 
            #.vars - mentioning the column names to mutate
            .funs = funs(confidence_to_num)) #applying the function

data_person$avg_conf <- rowMeans(data_person %>%
                                   select(sea_slug_conf:fragrant_orchid_conf))
```



```{r}
# TIME
#converting them to numeric
time_chr_to_num <- function(x){
  as.numeric(x)
}

data_person <- data_person %>% #choosing tibble
  mutate_at(.vars = vars(sea_slug_time: fragrant_orchid_time), 
            #.vars - mentioning the column names to mutate
            .funs = funs(time_chr_to_num)) #applying the function

#average time per image
data_person$avg_time_spent_per_Q <- 
rowMeans(data_person %>%
           select(sea_slug_time:fragrant_orchid_time))
```

The performance measures are below.

```{r}
#Creating a function for exact match columns.
exact_match_answer_to_num <- function(x){
  ifelse(x == "correct",1, 0) 
  #if response was categorized as "correct", assign 1, else 0.
}

#Mutating new columns to the tibble for exact match columns
data_person <- data_person %>% #choosing tibble
  mutate_at(.vars = vars(sea_slug: fragrant_orchid), 
            #.vars - mentioning the column names to mutate
            .funs = funs(`exact_match` = exact_match_answer_to_num,))
#.funs, letting it know to add new columns instead of replacing the values in
#the same column. It is achieved by setting `insert new name here` = function.

#Creating a function for synonym columns.
synonym_answer_to_num <- function(x){
  ifelse(x == "correct",1, ifelse(x == "synonym", 1, 0))
  #if response was categorized as "correct" or "synonym", assign 1, else 0.
}

#Mutating new columns to the tibble for synonym columns
data_person <- data_person %>%
  mutate_at(.vars = vars(sea_slug: fragrant_orchid),
            .funs = funs(`synonym` = synonym_answer_to_num,))

#Creating a function for present columns.
present_answer_to_num <- function(x){
  ifelse(x == "correct",1, ifelse(x == "synonym", 1, ifelse(x == "present", 1, 0)))
  #if response was categorized as "correct" or "synonym" or "present",
  #assign 1, else 0.
}

#Mutating new columns to the tibble for present columns
data_person <- data_person %>%
  mutate_at(.vars = vars(sea_slug: fragrant_orchid),
            .funs = funs(`present` = present_answer_to_num,))

#Creating a function for category columns.
category_answer_to_num <- function(x){
  ifelse(x == "correct",1, 
         ifelse(x == "synonym", 1, 
                ifelse(x == "present", 1, 
                       ifelse(x == "category", 1,  0))))
  #if response was categorized as "correct" or "synonym" or "present"
  #or "category", assign 1, else 0.
}

#Mutating new columns to the tibble for category columns
data_person <- data_person %>%
  mutate_at(.vars = vars(sea_slug: fragrant_orchid),
            .funs = funs(`category` = category_answer_to_num,))
```



```{r}
#Summing the number of correct answers every participant got.
#in each definition of accuracy

#exact match accuracy sum
data_person$exact_match_answers_sum <- 
  rowSums(data_person %>%
            select(sea_slug_exact_match:fragrant_orchid_exact_match), na.rm = TRUE)

#synonym_accuracy_sum
data_person$synonym_answers_sum <- 
  rowSums(data_person %>%
            select(sea_slug_synonym:fragrant_orchid_synonym), na.rm = TRUE)

#Present_accuracy_sum
data_person$present_answers_sum <- 
  rowSums(data_person%>%
           select(sea_slug_present:fragrant_orchid_present), na.rm = TRUE)
data_person$category_answers_sum <- 
  rowSums(data_person %>%
            select(sea_slug_category:fragrant_orchid_category), na.rm = TRUE)
```


```{r include=FALSE}
#Exact Match Accuracy
data_person$exact_match_answers_as_percent <- data_person$exact_match_answers_sum/24

#Synonym Accuracy
data_person$synonym_answers_as_percent <- data_person$synonym_answers_sum/24

#Present Accuracy
data_person$present_answers_as_percent <- data_person$present_answers_sum/24

#Category Accuracy
data_person$category_answers_as_percent <- data_person$category_answers_sum/24
```


```{r}
target <- c("1AI_nobar","1AI_bar","5AI_nobar","5AI_bar")
image_recog_AI1or5 <- data_person %>%
  filter(Group %in% target) %>%
  mutate(AI_1or5 = as_factor(case_when(Group == "1AI_nobar" ~ "1AI",
                             Group == "1AI_bar" ~ "1AI",
                             Group == "5AI_nobar" ~ "5AI",
                             Group == "5AI_bar" ~ "5AI"))) 
```


```{r}
#Reshaping row and columns
#Every row will be an image, each column will be a participant
data_image <- as.data.frame(t(data_person))
```


```{r}
#3 data_image_person - every row is an image for every participant.
data_image_person <- cbind(data_person %>%
        select(1:18,92:108,134:140,237:240), #selecting these columns so they remain untouched
                           stack(data_person %>%
                                   select(sea_slug_resp:fragrant_orchid_resp)), 
                           stack(data_person %>%
                                   select(sea_slug_conf:fragrant_orchid_conf)),
                           stack(data_person %>%
                                   select(sea_slug_time:fragrant_orchid_time)),
                           stack(data_person %>%
                                   select(sea_slug:fragrant_orchid)),
                           stack(data_person %>%
                                   select(sea_slug_exact_match:fragrant_orchid_exact_match)),
                           stack(data_person %>%
                                   select(sea_slug_exact_match:fragrant_orchid_exact_match)),
                           stack(data_person %>%
                                   select(sea_slug_synonym:fragrant_orchid_synonym)),
                           stack(data_person %>%
                                   select(sea_slug_present:fragrant_orchid_present)),
                           stack(data_person %>%
                                   select(sea_slug_category:fragrant_orchid_category)))

colnames(data_image_person)[47:62] <- c("response","image","conf_resp",
                                        "conf_name", "time_taken", "time_name",
                                        "image_accuracy", "image_name1",
                                        "exact_match","image_name2",
                                        "synonym","image_name3",
                                        "present","image_name4",
                                        "category","image_name5")
#pipe the enire thing.

data_image_person <- data_image_person %>% 
  select(-contains("name"))
```

# WRITE FILES
We want to create 3 files where the data are organized in the 3 different ways. 
The ASEM paper only uses data_person.
```{r}
#Writing Data Person file. Each row is a participant.Each column is an image.
write.csv(data_person,file="Data_cleaned_person.csv") #1 data_person version
write.csv(data_image, file = "data_cleaned_image.csv") #2 data_image version
write.csv(data_image_person, file = "data_cleaned_image_person.csv") #3 data_image_person version
```






